---
title: "Loops and Function"
author: "Andre Dextre"
date: "2022-08-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(skimr)
```

# Part 1: For Loops Revisited
## Task 1

```{r}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
transects <- c("Transect A", "Transect B", "Transect C")

week_trans <- matrix(nrow = length(weekdays), ncol = length(transects))

for (i in seq_along(transects)) {
  for (j in seq_along(weekdays)) {
    w_t <- paste(weekdays[j], "-", transects[i])
  week_trans[j, i] <- w_t
  }
}
```

# Part 2: Functions Introduced
## Task 2

Write a function called force that calculates a force (in Newtons), given inputs of mass (in kg) and acceleration (in ms2 (recall: F=ma), and returns a statement “The resulting force is ___ Newtons.”

```{r}
force <- function(mass, acceleration) {
    f <- mass * acceleration
    print(paste("The resulting force is", f, "Newtons" ))
}

force(mass = 10, acceleration = 34)
```

## Task 3

The length:weight relationship for fish is: `W=aL^b`, where where L is total fish length (centimeters), W is the expected fish weight (grams), and a and b are species-dependent parameter values (shown below for several fish from Peyton et al. 2016).

```{r}
sci_name <- c("Chanos chanos", "Sphyraena barracuda", "Caranx ignobilis")
common_name <- c("Milkfish", "Great Barracuda", "Giant trevally")
a_est <- c(0.0905, 0.0181, 0.0353)
b_est <- c(2.52, 3.27, 3.05)

fish_parms <- data.frame(sci_name, common_name, a_est, b_est)

fish_weight <- function(fish_name, tot_length) {
  fish_info <- filter(.data = fish_parms, common_name == fish_name)
  a = fish_info$a_est
  b = fish_info$b_est
  weight <- a * (tot_length^b)
  print(paste("The weight of the fish is", weight))
}

fish_weight("Milkfish", 23)
```

## Task 4

Wave power (more accurately wave energy flux) in deep water is approximated by:

Pdeep=0.5H2T
where P is power in kWm (potential power per wave meter), H is wave height in meters (more specifically, the significant wave height), and T is the wave period in seconds. Learn more here.

Write a function called wave_power that calculates potential ocean wave power given inputs of wave height and period.

Use your wave_power function to approximate wave power for a period of 8 seconds, over a range of wave heights from 0 to 3 meters by increments of 0.2 meters.

```{r}

```

